Papers_search

### 2019-02-07 R/Papers_search.Rmd
updated new subdirectories for the used files

```{r TI_book_fragment, echo=FALSE, fig.cap=" ", out.width='50%'}
knitr::include_graphics("./images/TI_book_fragment.png")
```
**Note**: LPS is a lipopolysaccharide that is constituent of the outer membranes of some bacteria and it is commonly used to trigger immune reaction without causing greater harm in animals.   
<br>

@@

These question refinements are leading us gently into deciding which studies to use in a meta-analysis. However, before we move onto inclusion criteria, it is wise to gather more intelligence (Unless you are already an expert on the topic).

@@

```{r WoS_adv_search, echo=FALSE, fig.cap=" ", out.width='100%'}
knitr::include_graphics("./images/WoS_adv_search.png")
```

@@

 1. Open Rayyan (we assume you already created a free account) and log in.    
 2. My Reviews -> New REVIEW...   
 3. Enter project title, e.g. "Terminal Investment"" and description, e.g. "test"."   
 4. Select files -> upload *Scopus10.ris* and press Continue.     
It may take several minutes for larger files and slower connections, but eventually the uploaded references should appear in the left panel under "Search methods" (you can upload more files with references via "Add new" link). Click on the "Uploaded References [scopus10.ris]" link in this panel to see the references in the right panel. Generally clicking on the links within panels on the left will filter the records in the right panels to include only highlighted sets (to get rid of the filter click on it again to remove highlighting).  
In the left panels there are several sub-panels.  
 5. In the "Keywords for include"" you can add (via "Add new" link) following terms (or at least a few of these): challenge, challenged, injected, injection, infected, infection, PHA, SRBC, vaccine (these terms will be highlighted green in the titles and abstracts to help them find more easily; Rayyan tries to populate this list by itself - but its algorithm is medical-centered so you should adjust this list for your projects).   
 6. "Keywords for exclude" - " set to: review, reviewed, model, human, people, women, men (these terms will be highlighted red in the titles and abstracts to help them find more easily; again, Rayyan tries to populate this list by itself).    
 7. Click on "All reviews" button in the top right corner to go to the project lists, then open your project again by choosing it from the list. A view with a pie chart (your screening progress) and a few buttons will appear. If you need to invite other people to do screening in parallel with you, do that by clicking on the "Invite" button. Stick with "Collaborator" selection and enter the email and message (e.g. "help me!"). Open your project again - you should see your collaborators added with some info on their work so far. Press on "Show" button to see the references view.  
 8. Click on the first review from the top - an abstract and other record info will appear in the bottom panel.  
 9. Using our abstract screening decision tree decide whether include this paper for the next stage of screening and press the "Include" or "Exclude" button accordingly. And do the assessment for the remaining records. As you go you can create and assign new labels to individual records, e.g.: "unsure/check". You could also enter reasons for exclusion, e.g. "human" (we normally don't do this as there are often hundreds or thousands of excluded records per project at this stage).  
10. Go to "All reviews" and check if other people finished their screening, if applicable. After that you can lift the "blind" mode (when collaborators cannot see each others decisions). For collaborative screens Rayyan will now provide filters to display all consensus included, consensus excluded and records with conflicting decisions. If you have any "conflicts" have a look again and discuss why you couldn't agree on a given record , come to agreement and make final decision. Export the records with final consensus decisions, for documentation, into a .csv file. You can filter the records into “Included” and just export those, also you can export them as a .bib or .ris file into a reference manager where you will collect full texts for the nest stage of the screening.

@@

**TASK 8:**  
It is time to do the full-text screening for the papers that passed title and abstract screening. There are some full-text papers that passed the initial screening in the directory - assess **Nielsen2012** and **Ardia2005** using our full-text screening decision tree. Hint: do not read the whole paper - just try to skim it and look for the key information.

>>>>

```{r TI_book_fragment, echo=FALSE, fig.cap=" ", out.width='50%'}
knitr::include_graphics("../images/TI_book_fragment.png")
```
**Note**: LPS is a lipopolysaccharide that is constituent of the outer membranes of some bacteria and it is commonly used to trigger immune reaction without causing greater harm in animals.   
<br>

@@

These question refinements are leading us gently into deciding which studies to use in a meta-analysis. However, before we move onto inclusion criteria, it is wise to gather more intelligence (unless you are already an expert on the topic).

@@

```{r WoS_adv_search, echo=FALSE, fig.cap=" ", out.width='100%'}
knitr::include_graphics("../images/WoS_adv_search.png")
```

@@

 1. Open Rayyan (we assume you already created a free account) and log in.    
 2. My Reviews -> New REVIEW...   
 3. Enter project title, e.g. "Terminal Investment"" and description, e.g. "test"."   
 4. Select files -> upload *Scopus10.ris* from the *data* sub-folder and press Continue.     
It may take several minutes for larger files and slower connections, but eventually the uploaded references should appear in the left panel under "Search methods" (you can upload more files with references via "Add new" link). Click on the "Uploaded References [scopus10.ris]" link in this panel to see the references in the right panel. Generally clicking on the links within panels on the left will filter the records in the right panels to include only highlighted sets (to get rid of the filter click on it again to remove highlighting).  
In the left panels there are several sub-panels.  
 5. In the "Keywords for include" you can add (via "Add new" link) following terms (or at least a few of these): challenge, challenged, injected, injection, infected, infection, PHA, SRBC, vaccine (these terms will be highlighted green in the titles and abstracts to help them find more easily; Rayyan tries to populate this list by itself - but its algorithm is medical-centered so you should adjust this list for your projects).   
 6. "Keywords for exclude" - " set to: review, reviewed, model, human, people, women, men (these terms will be highlighted red in the titles and abstracts to help them find more easily; again, Rayyan tries to populate this list by itself).    
 7. Click on "All reviews" button in the top right corner to go to the project lists, then open your project again by choosing it from the list. A view with a pie chart (your screening progress) and a few buttons will appear. If you need to invite other people to do screening in parallel with you, do that by clicking on the "Invite" button. Stick with "Collaborator" selection and enter the email and message (e.g. "help me!"). Open your project again - you should see your collaborators added with some info on their work so far. Press on "Show" button to see the references view.  
 8. Click on the first review from the top - an abstract and other record info will appear in the bottom panel.  
 9. Using our abstract screening decision tree decide whether include this paper for the next stage of screening and press the "Include" or "Exclude" button accordingly. And do the assessment for the remaining records. As you go you can create and assign new labels to individual records, e.g.: "unsure/check". You could also enter reasons for exclusion, e.g. "human" (we normally don't do this as there are often hundreds or thousands of excluded records per project at this stage).  
10. Go to "All reviews" and check if other people finished their screening, if applicable. After that you can lift the "blind" mode (when collaborators cannot see each others decisions). For collaborative screens Rayyan will now provide filters to display all consensus included, consensus excluded and records with conflicting decisions. If you have any "conflicts" have a look again and discuss why you couldn't agree on a given record , come to agreement and make final decision. Export the records with final consensus decisions, for documentation, into a .csv file. You can filter the records into “Included” and just export those, also you can export them as a .bib or .ris file into a reference manager where you will collect full texts for the nest stage of the screening.

@@

**TASK 8:**  
It is time to do the full-text screening for the papers that passed title and abstract screening. There are some full-text papers that passed the initial screening in the directory - assess **Nielsen2012** and **Ardia2005** (they are in "pdf" sub-folder) using our full-text screening decision tree. (Tip: do not read the whole paper - just try to skim it and look for the key information.)
